---
title: "Advent of Code 2023"
format: gfm
editor: source
execute:
  echo: false
  warning: false
  message: false
fig-dpi: 300
---

```{r}
library(tidyverse)
library(extrafont)
library(ggstar)

aoc_green <- "#009900"
aoc_gold <- "#ffff66"
github_grey <- "#0d1117"

# AoC-ish plot theme that blends into the GitHub dark mode
aoc_theme <- 
  theme(
    panel.background = element_rect(fill = NA, colour = NA, linewidth = 1),
    panel.grid = element_blank(),
    plot.background = element_rect(fill = github_grey, colour = github_grey),
    plot.title = element_text(colour = "white", size = 20, family = "Consolas"),
    strip.background = element_rect(fill = NA, colour = NA),
    strip.text = element_text(size = 16, colour = aoc_green),
    axis.text = element_text(size = 12, colour = "white", family = "Consolas"),
    axis.title = element_text(size = 14, colour = "white", family = "Consolas"),
    axis.line = element_line(colour = "white", linewidth = .5),
    axis.ticks = element_line(colour = "white", linewidth = .5),
    legend.position = "none"
  )

past_performance <- 
  data.frame(
    year = factor(2020:2022),
    stars = c(31, 33, 30)
  )
```

This repo contains my solutions for the [Advent of Code](https://adventofcode.com/) 2023 in `R`.

Here's my past performance:

```{r, fig.height=2.5}
past_performance %>% 
  ggplot(aes(x = year, y = stars)) +
  geom_star(fill = aoc_gold, size = 5) +
  geom_path(colour = aoc_gold, group = 1) +
  aoc_theme
```

However, this year is not really about performance, especially not when it comes to completion times. 
Most of the code in this repo was written using only one hand, because I'm nursing a three-month old baby with the other.

Follow me on [Bluesky](https://bsky.app/profile/juli-nagel.bsky.social), where I will post about my solutions as well!

## TOC

Here is a table of contents showing you what each day was about, along with some stats.
Completion time refers to the time it took me to complete the puzzle since release (part 1, and part 2 in brackets), as tracked on the Advent of Code website.
Next is my rank for the puzzle on that day (part 1 (part 2)), and finally the runtime of my code.
It's a crude measure of runtime[^1], where I simply calculate the difference in `Sys.time()` at the beginning and the end of part 1, and the beginning and end of part 2. 
That means in some occasions, the runtime for part 2 will be much shorter because part of the code needed to solve part 2 was already run in part 1. 
Reading in the data (and sometimes, basic preprocessing that has nothing to do with the puzzle solution) is excluded from the run time calculations.

[^1]: I know these stats are basically meaningless for anyone else's computer, but to put things into perspective, here are my computer stats: Razer Blade 15 Base Model, Intel Core i7-10750H CPU \@ 2.60GHz, 259 Mhz, 6 Cores, 12 Logical Processors, 16 GB RAM

| Day | Title                   | Completion Time     | Rank          | Run Time            |
|---------------|---------------|---------------|---------------|---------------|
| 1   | Trebuchet?!        | 02:15:03 (03:50:15) | 20750 (18843)   | 7.92 (83.07) ms     |
| 2   | Cube Conundrum        | 05:21:47 (05:27:15) | 34591 (32070)   | 85.35 (9.00) ms     |
